Using cosmic variance to constrain the dark matter halo mass of Lyman-alpha emitting galaxies at $z$=3.1

### 2013-05-21 paper/ms.tex
2 new paragraphs in the discussion section

The final 30 models can be distributed into two families of the same
size. The first, where the range $M_{\rm min}-M_{\rm max}$ is narrow,
typically of less than $<1.0$ dex. While in the second familiy the
extent $>1.0$ dex. In the first case the minimum halo mass is found to
be in a wide range $10^{10}\hMsun <M_{\rm min}< 10^{11.5}\hMsun$ while
in the second case, only models with $M_{\rm min}\sim 10^{10.9}\hMsun$
are compatible with the observational contraints. In what follows we
discuss the implications of the existence of these two families of
models.

@@

>>>>

These 30 models can be classified into two families of the same
size. The first, where the range $M_{\rm min}-M_{\rm max}$ is narrow,
typically of less than $<1.0$ dex. While in the second familiy the
extent $>1.0$ dex. In the first case the minimum halo mass is found to
be in a wide range $10^{10}\hMsun <M_{\rm min}< 10^{11.5}\hMsun$ while
in the second case, only models with $M_{\rm min}\sim 10^{10.9}\hMsun$
are compatible with the observational contraints. In what follows we
discuss the implications of the existence of these two families of
models.

@@

In the case of a narrow of masses to host LAEs the upper masses are
bound to be $M_{\rm max}< 10^{11.5}$\hMsun as it is show in Figure
\ref{figure:mock_and_f_occ}. For halos more massive than this bound it
is naturally expected that the galaxies can be observed as Lyman Break
Galaxies (LBGs). This would imply that not all the bright LBGs can
detected as a LAE.

We have the opposite situation in the second familiy of models. If
we have a wide range in halo masses, where the upper end of the halo
masses can be considered as observed LAEs, one can expect that bright
LBGs will have a correspondence as observed LAEs. The most interesting
aspect is that there is a clear cut in the minimal mass that can be
attained by observed LAEs $M_{\rm min}> 10^{11}$\hMsun. This puts a tight
constraint on the relationship between the minimum star formation rate
required to be observed as a LAE and this minimal halo mass.
